D3064R0: How to Avoid OOTA Without Really Trying

### 2024-04-04 ootavacuous.tex
C has bracket on next line, litmus tests on same line
Reported-by: Alan Stern <stern@rowland.harvard.edu>
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

\begin{listing}
\begin{verbatim}
 1 atomic<int> x, y;
 2
 3 void thread1() {
 4   int r1 = x.load(memory_order_relaxed);
 5   y.store(r1, memory_order_relaxed);
 6 }
\end{verbatim}
\caption{Non-Volatile Accesses and Dependencies}
\label{lst:Non-Volatile Accesses and Dependencies}
\end{listing}

Because both \co{x} and \co{y} are nonvolatile, a C++ compiler is
free to assume that the value loaded by line~4 will be either some value
stored to \co{x} or its initial value.
And because there are no stores to \co{x}, the only remaining possibility
is the default-initialized value of zero.
Therefore, the compiler is within its rights to substitute
the constant zero for \co{r1} on line~5, eliminating the semantic
dependency that would otherwise extend from line~4 to line~5.

\begin{listing}
\begin{verbatim}
 1 volatile atomic<int> x, y;
 2
 3 void thread1() {
 4   int r1 = x.load(memory_order_relaxed);
 5   y.store(r1, memory_order_relaxed);
 6 }
\end{verbatim}
\caption{Volatile Accesses and Dependencies}
\label{lst:Volatile Accesses and Dependencies}
\end{listing}

One way to preserve this dependency is use of \co{volatile}, as shown in
Listing~\ref{lst:Volatile Accesses and Dependencies}.
Now the compiler is forbidden from assuming that the value loaded
by line~4 has any relation to any stores to or initialization of \co{x}.

>>>>

\begin{listing}
\begin{verbatim}
 1 atomic<int> x, y;
 2
 3 void thread1()
 4 {
 5   int r1 = x.load(memory_order_relaxed);
 6   y.store(r1, memory_order_relaxed);
 7 }
\end{verbatim}
\caption{Non-Volatile Accesses and Dependencies}
\label{lst:Non-Volatile Accesses and Dependencies}
\end{listing}

Because both \co{x} and \co{y} are nonvolatile, a C++ compiler is
free to assume that the value loaded by line~5 will be either some value
stored to \co{x} or its initial value.
And because there are no stores to \co{x}, the only remaining possibility
is the default-initialized value of zero.
Therefore, the compiler is within its rights to substitute
the constant zero for \co{r1} on line~6, eliminating the semantic
dependency that would otherwise extend from line~5 to line~6.

\begin{listing}
\begin{verbatim}
 1 volatile atomic<int> x, y;
 2
 3 void thread1()
 4 {
 5   int r1 = x.load(memory_order_relaxed);
 6   y.store(r1, memory_order_relaxed);
 7 }
\end{verbatim}
\caption{Volatile Accesses and Dependencies}
\label{lst:Volatile Accesses and Dependencies}
\end{listing}

One way to preserve this dependency is use of \co{volatile}, as shown in
Listing~\ref{lst:Volatile Accesses and Dependencies}.
Now the compiler is forbidden from assuming that the value loaded
by line~5 has any relation to any stores to or initialization of \co{x}.
